Community context determines competition/facilitation trade-offs in pollination systems

### 2019-04-23 paper/manuscript.Rmd
Some extra refs

At the community scale, the factors that determine the patterns of conspecific and heterospecific pollen deposition are tightly intertwined, operate simultaneously, and may lead to emergent phenomena not observed at smaller scales [@flanagan_effects_2011]. 
For instance, recent empirical evidence suggests that plants with flowering traits that are "original" relative to others in the community generally have fewer interaction partners [@coux_linking_2016]. 
This evidence is aligned with the notion that a species which interacts with few species does so strongly with each of them whereas a species that interacts with a large number of species does so comparatively weakly (TODO: ref needed). 
If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollinators in species with "original" traits and an increase of competition in species with a large number of interaction partners [@gibson_can_2012]. 
Alternatively, it might also be the case that density (for example in terms of flower or pollen counts) is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987] but might also receive more effective visits by capitalising on a larger share of both visits and the pollen carried by pollinators. 
In this case, a potential reduction in the absolute amount of conspecific pollen received could be compensated by an increase in the amount of conspecific pollen relative to heterospecific pollen. 
Altogether, it is clear that some ecological factors can influence pollen deposition and that these factors, in the specific context of pollination, could be used to roughly define a species *realised niche* in their community. 
However, the intertwined nature of these factors makes it hard to determine whether they favour or hinder the pollination service at the community level. 
Moreover, their relative importance has not yet been empirically evaluated in natural plant communities.

>>>>

At the community scale, the factors that determine the patterns of conspecific and heterospecific pollen deposition are tightly intertwined, operate simultaneously, and may lead to emergent phenomena not observed at smaller scales [@flanagan_effects_2011]. 
For instance, recent empirical evidence suggests that plants with flowering traits that are "original" relative to others in the community generally have fewer interaction partners [@coux_linking_2016]. 
This evidence is aligned with the notion that a species which interacts with few species does so strongly with each of them whereas a species that interacts with a large number of species does so comparatively weakly (TODO: ref needed). 
If evolutionary specialisation occurs by changing traits to focus on fewer but better partners [@caruso_competition_2000], we should expect a reduction of competition for pollinators in species with "original" traits and an increase of competition in species with a large number of interaction partners [@gibson_can_2012; @carvalheiro_potential_2014]. 
Alternatively, it might also be the case that density (for example in terms of flower or pollen counts) is the dominant force driving pollen transfer [@seifan_outcome_2014]. 
Abundant plant species might experience a dilution of available pollinators [@feinsinger_effects_1987] but might also receive more effective visits by capitalising on a larger share of both visits and the pollen carried by pollinators. 
In this case, a potential reduction in the absolute amount of conspecific pollen received could be compensated by an increase in the amount of conspecific pollen relative to heterospecific pollen. 
Altogether, it is clear that some ecological factors can influence pollen deposition and that these factors, in the specific context of pollination, could be used to roughly define a species *realised niche* in their community. 
However, the intertwined nature of these factors makes it hard to determine whether they favour or hinder the pollination service at the community level. 
Moreover, their relative importance has not yet been empirically evaluated in natural plant communities.
